\section{Shared Part}

This could be the Shared Part of the document. It is designed to be written by all members of the team.

Each member should ideally write their details in the table of contributors in the Shared Part of the document.

\subsection{Comments from the first student}
Well, the module has happened, isn't that great, we have the ability to remember a whole bunch of \textbf{bunches} of diagram types, \textbf{bought} a book for the expected reading to find out that all of the expected reading was provided with the sources of these documents looking \textbf{less legitimate} each passing week. But the labs, for the \textbf{labs} and the teamwork it has all been worth it.


\subsection{Comments from the second student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Comments from the third student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Comments from the forth student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Comments from the fifth student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Table of Contributors}


If you want to move a table around you will need to put some parameters in square brackets, if you want it exactly where it is positioned in the text editor just uncomment the [h] below, just after begin{table}

This is the table of contributors (Table~\ref{authors}):
\begin{table}[h]
\centering
\caption{People in the Group}
\label{authors}
\begin{tabular}{|l|l|}
\hline
\textbf{Name} & \textbf{ID} \\
\hline Joshua 
& 4297979\\ 
\hline
& \\
\hline
& \\
\hline
& \\
\hline
& \\
\hline
\end{tabular}
\end{table}